\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-14 trunk/arch.tex
Added a figure showing state  flow between 2 reactors

\item In order to identify its current {\em internal} state values the
  \textsf{Pilot} \comment{double check this mod} needs to know the
  current {\em external} state information it relies on. In this case
  the current \textsf{Waypoint} the vehicle is heading to can be
  extracted for example from the current \textsf{Nav\_cmd} executed.

@@

@@

\item \texttt{step} that accepts new goals requested (if any) on the
  {\em internal} timeline of a reactor and will execute one step of
  deliberation. In the context of Europa for example pone step of
  deliberation correspod to resolve one sibngle flaw while ensuring
  that the resulting plan is not proven inconsistent. This implies
  that it also includes the backtracking of the search in such case. 
  The returned value by this step function is a boolean which
  indicates whether the reactor needs some extra step to deliberate or
  if this last step resulted on a complete plan for the reactor
  look-ahead. On the later, the part of the plan that concern this
  reactor {\em external} timelines is provided in order to be
  dispatched as goals to whichever reactor that is reponsible for
  these. \comment{By extending I may have saud things I developped
    below ... will have  to check}
\end{itemize}

Both these deliberative functions have different scope and temporal
constraints. The \texttt{synchronize} call is considered as atomic and
will focus only on state inference for the current tick by identifying
the current value of {\em internal} state variables from the latest
updates on the {\em external} state variables. This process propagates
up in the reactor dependency graph at every tick to ensure that all
reactors are aware of the current state of the world. \texttt{step}
relates to a single decision step of the planning process which is
focused on the future evolution of state variables; it can take
multiple steps spanning multiple ticks for a reactor to produce a plan
that is both complete and valid. When such plan is identified
\comment{how? Is there a terminating condition? No more flaws but I
  washoping it would have been defined in europa section} its {\em external}
timeline(s) are then dispatched to the corresponding reactors which
own these times and which in turn can start their own deliberation
\texttt{step}s to satisfy these new objectives. Consequently execution
occurs as these goals and plans propagate down in the reactor
hierarchy until they eventually become goals for the lowest level
reactor which -- instead of deliberating -- may just transform this
goal into a command for execution in hardware.

@@

In the europa based reactor we introduce this decision reuqirement 
as a new type of flaw for the europa framework. This flaw enforces at the
reactor to identify fully its internal state for the current tick. By
using this new flaw we can describe the synchronization process as
this general sequence :

>>>>

\item In order to identify its current {\em internal} state values the
  \textsf{Pilot} needs to know the current {\em external} state 
  information it relies on. This information is providede in turn by
  the reactors that provided these timelines as {\em internal}. In
  this specific case, the current \texttt{Waypoint} where the vehicle
  is heading can be evaluated based on the \texttt{Nav\_cmd} executed
  along with usefull \texttt{Sensor\_Data}, both being provided by the
  \texttt{Vehicle} reactor.

@@

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=0.45\columnwidth]{figs/TREX_flow}
  \vskip-1cm
  \caption{Illustration of state information flow between the
    \texttt{Pilot} and the \texttt{Vehicle} reactors.
    Observations transit in a bottom-up during synchronization 
    and apply to the execution frontier $\tau$. 
    Goal information flow from the top to the bottom and concern the
    desired future values of state variables.}
  \label{fig:trex:flow}
\end{figure}

@@

\item \texttt{step} that accepts new goals requested (if any) on the
  {\em internal} timeline of a reactor and will execute one step of
  deliberation. In the context of \eu for example pone step of
  deliberation correspod to resolve one sibngle flaw while ensuring
  that the resulting plan is not proven inconsistent. This implies
  that it also includes the backtracking of the search in such case. 
  The returned value by this step function is a boolean which
  indicates whether the reactor needs some extra step to deliberate or
  if this last step resulted on a complete plan for the reactor
  look-ahead. On the later, the part of the plan that concern this
  reactor {\em external} timelines is provided in order to be
  dispatched as goals to whichever reactor that is reponsible for
  these. \comment{By extending I may have saud things I developped
    below ... will have  to check}
\end{itemize}

Both these deliberative functions have different scope and temporal
constraints. The \texttt{synchronize} call is considered as atomic and
will focus only on state inference for the current tick by identifying
the current value of {\em internal} state variables from the latest
updates on the {\em external} state variables. This process propagates
up in the reactor dependency graph at every tick to ensure that all
reactors are aware of the current state of the world. \texttt{step}
relates to a single decision step of the planning process which is
focused on the future evolution of state variables; it can take
multiple steps spanning multiple ticks for a reactor to produce a plan
that is both complete and valid. When such plan is identified
\comment{how? Is there a terminating condition? No more flaws but I
  washoping it would have been defined in \eu section} its {\em external}
timeline(s) are then dispatched to the corresponding reactors which
own these times and which in turn can start their own deliberation
\texttt{step}s to satisfy these new objectives. Consequently execution
occurs as these goals and plans propagate down in the reactor
hierarchy until they eventually become goals for the lowest level
reactor which -- instead of deliberating -- may just transform this
goal into a command for execution in hardware.

@@

In the \eu based reactor we introduce this decision reuqirement 
as a new type of flaw for the \eu framework. This flaw enforces at the
reactor to identify fully its internal state for the current tick. By
using this new flaw we can describe the synchronization process as
this general sequence :
